Alpine indices

### 2020-05-19 doc/indices report/indices report.Rmd
full filled seed mass embryo

# Number of records with >80% germination and germination indices, by region.

@@

# Number of records with >80% germination and germination indices, by alpine strict vs. generalist.

>>>>

# Number of records with >90% germination and germination indices, by region.

@@

# Number of records with >90% germination and germination indices, by alpine strict vs. generalist.
